Exact asymptotic expressions for local clustering in hyperbolic random graphs \\ \TM{ I prefer not to use the term ``hyperbolic random graph". Better : KPKVB random graph or, in the title,``a hyperbolic model of complex networks"}

### 2019-01-10 paper.tex
a couple of comments in section 1
Merging Tobias' comments

\title{Exact asymptotic expressions for local clustering in hyperbolic random graphs}
\author[1]{Nikolaos Fountoulakis}
\author[2]{Pim van der Hoorn}
\author[3]{Tobias M\"{u}ller}
\author[3]{Markus Schepers}

@@

>>>>

\title{Exact asymptotic expressions for local clustering in hyperbolic random graphs \\ \TM{ I prefer not to use the term ``hyperbolic random graph". Better : KPKVB random graph or, in the title,``a hyperbolic model of complex networks"}}
\author[1]{Nikolaos Fountoulakis}
\author[2]{Pim van der Hoorn}
\author[3]{Tobias M\"{u}ller}
\author[3]{Markus Schepers}

@@

\TM{ Maybe a ``conclusion and further work'' section here,  before the references and appendix? \\
Also, appendix usually comes after references in my experience.}
